#####################################################################################################
# File: indep_snps.rmd
#
# Created by Jeanne N. Samake on June 2022 
# Based on script originally written by Philip Lavretsky 
# For use in R
#
# Description: Filter bi-allelic SNPs for singletons and snps in linkage disequilibrium 
# to generate an #independent bi-allelic SNPs dataset in PLINK format.
#
#NOTE: This script requires PLINK v1.9
#####################################################################################################

#Run Plink
#(1) Filter SNPs for singletons (--maf 0.004), any SNP missing >20% of data across samples (--geno 0.2), and pairwise analysis of LD (--indep-pairwise 2 1 0.5) in which one of two linked SNPs is randomly excluded if an LD correlation factor (r2)>0.5 is obtained. 
```{r }
system("./plink --file autosomal.plink --allow-extra-chr --maf 0.004 --geno 0.20 --indep-pairwise 2 1 0.5 --allow-no-sex --noweb --out autosomal.plink")
```

#(2) Prune out/in
```{r }
system("./plink --file autosomal.plink --maf 0.004 --geno 0.20 --extract autosomal.plink.prune.in --allow-no-sex --make-bed --out autosomal.plink.INDEP --noweb")
```


#(3) Final dataset
```{r }
system("./plink --file autosomal.plink --maf 0.004 --geno 0.20 --extract autosomal.plink.prune.in --allow-no-sex --recode --out autosomal.plink.INDEP --noweb")
```



